Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-04-22 latex/ICPP21/paper.tex
updated formatting for ICPP

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{ifthen}
\usepackage{flushend}

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand*{\email}[1]{\href{mailto:#1}{\nolinkurl{#1}} } 
\newcommand{\dims}[1]{\langle #1 \rangle}

@@

\begin{document}

\bstctlcite{IEEE:BSTcontrol}

@@

\author{\IEEEauthorblockN{Grey Ballard}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston-Salem, NC, USA \\
\email{ballard@wfu.edu}}
\and
\IEEEauthorblockN{Jack Weissenberger}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston-Salem, NC, USA \\
\email{jack.weissenberger@gmail.com}}
\and
\IEEEauthorblockN{Luoping Zhang}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Wake Forest University}\\
Winston-Salem, NC, USA \\
\email{zhanl317@wfu.edu}}
}

\maketitle

@@

@@

\paragraph*{Acknowledgments}

This material is based upon work supported by the NSF Grant No. CCF1942892 and a Wake Forest University Undergraduate Research and Creative Activities (URECA) Research Fellowship.

\vspace{-.175cm}

\bibliographystyle{IEEEtran}
\bibliography{refs}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{ifthen}
\usepackage{balance}

@@

\newcommand{\dims}[1]{\langle #1 \rangle}

@@

\acmConference[ICPP'21]{International Conference on Parallel Processing}{August 9--12}{Chicago, IL, USA}

@@

%\author{\IEEEauthorblockN{Grey Ballard}
%\IEEEauthorblockA{\textit{Department of Computer Science} \\
%\textit{Wake Forest University}\\
%Winston-Salem, NC, USA \\
%\email{ballard@wfu.edu}}
%\and
%\IEEEauthorblockN{Jack Weissenberger}
%\IEEEauthorblockA{\textit{Department of Computer Science} \\
%\textit{Wake Forest University}\\
%Winston-Salem, NC, USA \\
%\email{jack.weissenberger@gmail.com}}
%\and
%\IEEEauthorblockN{Luoping Zhang}
%\IEEEauthorblockA{\textit{Department of Computer Science} \\
%\textit{Wake Forest University}\\
%Winston-Salem, NC, USA \\
%\email{zhanl317@wfu.edu}}
%}

@@

\begin{document}
\maketitle

@@

%\paragraph*{Acknowledgments}
%
%This material is based upon work supported by the NSF Grant No. CCF1942892 and a Wake Forest University Undergraduate Research and Creative Activities (URECA) Research Fellowship.

\newpage
\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}
